---
title: "textab: Create Highly-Customized LaTeX tables in R" 
output: github_document
knit: (function(inputFile, encoding) {
        Sys.setenv(RSTUDIO_PANDOC='/Applications/RStudio.app/Contents/Resources/app/quarto/bin/tools');
        rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), "README.md")) })
--- 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Created by Thibaut Lamadon and Bradley Setzler

The `textab` package produces highly-customized LaTeX tables in R. 

There are only three functions in this package:

  - `TexRow`: Form a row in a LaTeX tabular environment.
  - `TexSave`: Save the tabular as a .tex file, and optionally compile it as a PDF.
  - `TexMidrule`: Insert a midrule, or list of partial midrules, between rows in a LaTeX tabular environment.
  

This package builds LaTeX tables in blocks, in the spirit of `ggplot2`, using
the `+` and `-` operators for concatenation.

  - minus sign (`-`): Combine rows side-by-side (forming a wider row).
  - plus sign (`+`): Stack rows vertically (for multiple rows).


To install the package:

```{r echo=T, eval=FALSE, message=FALSE}
devtools::install_github("setzler/textab")
```

To use the package after it is installed:

```{r echo=T, eval=TRUE, message=FALSE}
library(textab)
```

To get started, read the following articles:

- [Get Started](https://setzler.github.io/textab/articles/textab.html)
- [Function Documentation](https://setzler.github.io/textab/reference/index.html).
- [Formatting Numbers](https://setzler.github.io/textab/articles/Numerics.html).



